Simultaneous segmentation and distortion correction on diffusion weighted MR using shape priors

### 2012-12-19 Publications/2013-IPMI/Latex/045-Experiments.tex
Added FA, MD formulae

\paragraph{Derived scalar features}
The target \ac{dwi} data is characterized by its distortions and its
low resolution (typically around $2.2x2.2x3mm^3$). Depending on the
posterior reconstruction methodology and the angular resolution
intended, the \ac{dwi} raw data has to be processed in order to
extract the information in a manageable manner. The properties of
the reconstructed tensors and derived scalar maps have been
studied by \cite{ennis_orthogonal_2006}. Based on their
findings, the proposed energy model adapts to the \ac{fa} and \ac{md}
for their properties. Whereas \ac{fa} describes the \emph{shape} of diffusion, 
the \ac{md} depicts the \emph{magnitude} of the process.

\textbf{FIXME: can you give the respective formula, how you get from the above signal to FA/MD?}
\begin{equation}
FA = \sqrt{ \frac{3}{2}},\frac{\sqrt{ (\lambda_1 - \hat{\lamda})^2 + (\lambda_2 - \hat{\lamda})^2 + (\lambda_3 - \hat{\lamda})^2}}{\sqrt{ {\lambda_1}^2 + {\lambda_2}^2 + {\lambda_3}^2}}
\end{equation}

>>>>

\paragraph{Derived scalar features}
The target \ac{dwi} data is characterized by its distortions and its
low resolution (typically around $2.2x2.2x3mm^3$). Depending on the
posterior reconstruction methodology and the angular resolution
intended, the \ac{dwi} raw data has to be processed in order to
extract the information in a manageable manner. The properties of
the reconstructed tensors and derived scalar maps have been
studied by \cite{ennis_orthogonal_2006}. Based on their
findings, the proposed energy model adapts to the \ac{fa}~\eqref{eq:fa} 
and \ac{md}~\eqref{eq:md} for their properties. 
Whereas \ac{fa} \ describes the \emph{shape} of diffusion, 
the \ac{md} depicts the \emph{magnitude} of the process.

\begin{align}
\mathrm{FA} &= \sqrt{ \frac{1}{2}}\,\frac{\sqrt{ (\lambda_1 - \lambda_2)^2 + (\lambda_2 - \lambda_3)^2 + (\lambda_3 - \lambda_1)^2}}{\sqrt{ {\lambda_1}^2 + {\lambda_2}^2 + {\lambda_3}^2}} \label{eq:fa} \\
\mathrm{MD} &= ( \lambda_1 + \lambda_2 + \lambda_3 ) / 3 \label{eq:md}
\end{align}
